---
title: "Foraging motion analysis - Fitting statistical models"
author: "kostas lagogiannis"
date: "20/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The data on dispersion, MSD and mean-path lengths suggest differences between groups. 
To rigorously compare the different treatments I next fit statistical models to: 

  - Compare difference in mean speed: mean path-length vs path duration 
  - MSD vs Time -power-laws - check exponents
  - Probability of being in ROI against time

\[
D^G \sim \mathcal{N}(\mu^G,\sigma^G)\\
k_c \sim \mathbb{categorical}(\lambda)\\
d_l \sim \mathcal{N}(\mu_{k[c]},\sigma_{k[c]})
\]
where the $\sum^{K}_{k=1}\lambda_k = 1$.


```{r jagsmodelfitting-code-setup,eval=FALSE, include=FALSE}
## Because the Full Dispersion Record data is too large- I use a sparse subsampled version to cluster the motin
## this works because movement at 0.5 sec intervals should be sufficient to classify the  larva's dispersion   over the last 5 sec
# nsamp allows a quick random subset to be created for testing purposes .
makeDispersionDataInferenceSet <- function(bQuickTest = FALSE,nsamp=4000)
{
  #nsubsample <- 10000 
  ##Subsample The Dispersion Data into 0.5 sec bins - But Add the hunt Event Frames
  loadDispersionData()
  datSubDispersion  <- datDispersion[ !is.na(datDispersion$Dispersion), ]
  datSubDispersion <- datSubDispersion[seq(1,NROW(datSubDispersion),by=nsubsampleInterval ),]
  # add the exact frames of hunt events so we can cluster them in exploit/Explore easly datHEventDispersion$frameRow
  # Frame Records of Huntevents not in SubSampled frames
  missinghuntEvents.frameROW <- datHEventDispersion[!(datHEventDispersion$frameRow %in% datSubDispersion$frameRow),"frameRow"] 
  # Merge missing hunt Frames onto subsampled dispersion data so we can cluster Hunt Events Specifically
  datSubDispersion <- rbind(datSubDispersion,datDispersion[datDispersion$frameRow %in% missinghuntEvents.frameROW,])
  
  #Add Hunt Initiation Events
  datSubDispersion$HuntMode <- 0
  datSubDispersion[datSubDispersion$frameRow %in% datHEventDispersion$frameRow,"HuntMode"] <- 1
  ## Lastly / Model and Cluster All Data so we can then run a relative comparison between groupscompare

  if (bQuickTest)
      datSubDispersion   <- datSubDispersion[sample(1:NROW(datSubDispersion),nsamp),]
  
  return(datSubDispersion)
}

```

The GM model is implemented in RJags and its code is as as follows:
```{r RJags-model-DEF,eval=FALSE,include=TRUE,ref.label='clustering-code-setup'}
strDispersionClusterModel <- "
var initR[1,Nclust];
model {
    # Likelihood: 
    for( i in 1 : N ) {
      y[i] ~ dnorm( muOfClust[ clust[i] ], tauOfClust[ clust[i] ] )
      #mu[i] <-  ]
      clust[i] ~ dcat( pClust[1:Nclust] )
    }
    
    # Prior:
    for ( clustIdx in 1: Nclust ) {
      muOfClust[clustIdx]  ~ dnorm( 0 , 1.0E-10 )
      tauOfClust[clustIdx] ~ dgamma( 0.01 , 0.01 )
      initR[1,clustIdx] <- 1
    }
    pClust[1:Nclust] ~ ddirch( initR )
}

"
```


```{r RJags-model-RUN, eval=FALSE, include=FALSE,ref.label='clustering-code-setup'}

initfunct <- function(nchains,N)
{
  initlist <- replicate(nchains,list(#mID=c(rbinom(N,1,0.5)), 
#                                     sigma = matrix(c (  c(runif(1,min=0,max=0.1),runif(1,min=0,max=2)),
#s                                                         c(runif(1,min=0,max=0.1),runif(1,min=0,max=15))  ),nrow=2,byrow=T  ),
#                                     mu  = matrix(c (  c( rnorm(1,mean=1,sd=sqrt(1/10) ), rnorm(1,mean=8,sd=sqrt(1/2) ) ),
#                                                        c( rnorm(1,mean=1, sd=sqrt(1/10) ) , rnorm(1,mean=30, sd=sqrt(1/0.1) )    ) )
#                                                     ,nrow=2,byrow = T  ),
                                     ".RNG.name"="base::Super-Duper",
                                     ".RNG.seed"=round(runif(1,0,60000)) ),
                                     simplify=FALSE)
  return(initlist)
}

datSubDispersion <- makeDispersionDataInferenceSet(FALSE)

vDispersion.NF.E <- datSubDispersion[datSubDispersion$groupID == 'NL',"Dispersion",]
vDispersion.LF.E <- datSubDispersion[datSubDispersion$groupID == 'LL',"Dispersion",] 
#vDispersion.NF.E <- sample(datSubDispersion[datSubDispersion$groupID == 'NL',"Dispersion",] ,min(nsubsample,NROW(datSubDispersion[datSubDispersion$groupID == 'NL',]) )  )
vDispersion.DF.E <- datSubDispersion[datSubDispersion$groupID == 'DL',"Dispersion",]

vDispersion.NF.S <- datSubDispersion[datSubDispersion$groupID == 'NE',"Dispersion",]  
vDispersion.LF.S <- datSubDispersion[datSubDispersion$groupID == 'LE',"Dispersion",]
vDispersion.DF.S <- datSubDispersion[datSubDispersion$groupID == 'DE',"Dispersion",]


runGaussianMixClusterModel <- function(vDispersion)
{
  ##Cluster Membership
  N = NROW(vDispersion)
  Nclust <- 2
  clust = rep(NA,N) 
  clust[which.min(vDispersion)]=1 # smallest value assigned to cluster 1
  clust[which.max(vDispersion)]=2 # highest value assigned to cluster 2 
  
  dataList = list(
      y = vDispersion ,
      N = N,
      Nclust = 2 ,
      clust = clust 
      #onesRepNclust = rep(1,Nclust)
  )
  ##
  ##
  steps <-500
  nchains <- 3
  nthin <- 10
  #str_vars <- c("mu","rho","sigma","x_rand") #Basic model 
  str_vars <- c("clust","pClust","muOfClust","tauOfClust") #Mixture Model
  
  # Run the 2 chains in parallel (allowing the run.jags function
  # to control the number of parallel chains). We also use a
  # mutate function to convert the precision to standard deviation:
  results <- run.jags(model=strDispersionClusterModel, n.chains=nchains,
                         inits=initfunct(nchains,dataList$N),
                         thin=nthin,
                         sample=steps,
                         data= dataList,
                         monitor=str_vars,
                         method="parallel", mutate=list("prec2sd", vars="tauOfClust"))
 return(results) 
}


results.NF.E <- runGaussianMixClusterModel(vDispersion.NF.E)
write.jagsfile(results.NF.E, file=paste0(strDataExportDir,'jagsModel_clustDispersion_NL.txt') )
save(list=c("results.NF.E","vDispersion.NF.E"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_NL.RData') )

results.LF.E <- runGaussianMixClusterModel(vDispersion.LF.E)
write.jagsfile(results.LF.E, file=paste0(strDataExportDir,'jagsModel_clustDispersion_LL.txt') )
save(list=c("results.LF.E","vDispersion.LF.E"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_LL.RData') )

results.DF.E <- runGaussianMixClusterModel(vDispersion.DF.E)
write.jagsfile(results.DF.E, file=paste0(strDataExportDir,'jagsModel_clustDispersion_DL.txt') )
save(list=c("results.DF.E","vDispersion.DF.E"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_DL.RData') )

## Spont
results.NF.S <- runGaussianMixClusterModel(vDispersion.NF.S)
write.jagsfile(results.NF.S, file=paste0(strDataExportDir,'jagsModel_clustDispersion_NE.txt') )
save(list=c("results.NF.S","vDispersion.NF.S"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_NE.RData') )

results.LF.S <- runGaussianMixClusterModel(vDispersion.LF.S)
write.jagsfile(results.LF.S, file=paste0(strDataExportDir,'jagsModel_clustDispersion_LE.txt') )
save(list=c("results.LF.S","vDispersion.LF.S"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_LE.RData') )

results.DF.S <- runGaussianMixClusterModel(vDispersion.DF.S)
write.jagsfile(results.DF.S, file=paste0(strDataExportDir,'jagsModel_clustDispersion_DE.txt') )
save(list=c("results.DF.S","vDispersion.DF.S"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_DE.RData') )
  
  resultsGmix.All <- runGaussianMixClusterModel(datSubDispersion$Dispersion)
  write.jagsfile(resultsGmix.All, file=paste0(strDataExportDir,'jagsModel_clustDispersion_ALL.txt') )
  save(list=c("resultsGmix.All","datSubDispersion"),file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_All.RData') )


##Convergence Check
muclustNF <- as.mcmc.list(results.NF.S, vars="muOfClust")
plot(muclustNF)

# View the results using the standard print method:
#summary(results.LF.E)

```

and the clustering results  of each group/condition are summarized in the following figures:

```{r RJags-model-PLOT,   fig.show='hide', out.width="33%", eval=FALSE, include=FALSE, cache=FALSE, dev='png'}
#ref.label='clustering-code-setup'
##
library(rjags)
library(runjags)
library('coda')

loadDispersionData()

## Extracts the monitor values and returns them packaged in a list
getMCMCEstimatedParams <- function(results,groupID,ichain = 2)
{
  clustcoeff = as.mcmc.list(results, vars="clust")
  tauOfClust = as.mcmc.list(results, vars="tauOfClust")
  muOfClust = as.mcmc.list(results, vars="muOfClust")
  lret <- list(
  chain =  ichain,
  groupID = groupID,
  muOfClustcoeff = muOfClust,
  tauOfClustcoeff = tauOfClust,
  mean = muOfClust[[ichain]],
  sd = cbind(tauOfClust[[ichain]][,3],tauOfClust[[ichain]][,4]), ##Take the precision converted to sd Columns 
  pClustcoeff = as.mcmc.list(results, vars="pClust"),
  clustID = round(colMeans(clustcoeff[[ichain]]) ) 
  )
  
  return (lret)
}


#  clusterIDOffset, and groupIDOffset plot Allows function to work when multiple subgroups are modelled
# by extracting from these columns pClust[groupID,Clust] : pClust[1,1] pClust[2,1] ... pClust[5,2] pClust[6,2] 
plotClusterProb <- function(lmcmcRes,clustCol,groupIDOffset=1,clustIDOffset=1)
{
   ##plot prob of occupying each cluster
  breaksProb <- seq(0,1.01,by=0.01)
  list_histo <- hist(lmcmcRes$pClustcoeff[[lmcmcRes$chain]],breaks=breaksProb,plot=FALSE )
  h1<-hist( lmcmcRes$pClustcoeff[[lmcmcRes$chain]][,groupIDOffset], breaks=breaksProb,plot=FALSE) ##Cluster 1 ylim=c(0,max(list_histo$counts))
  h2 <- hist( lmcmcRes$pClustcoeff[[lmcmcRes$chain]][,groupIDOffset + clustIDOffset], breaks=breaksProb, plot=FALSE ) ## ##Cluster 1 
  
  ##Colour Determines which Cluster is fast and slow
   barplot(rbind(h1$density,h2$density),beside = FALSE, col = c(clustCol[1],clustCol[2],"white"),
           names.arg = (h1$breaks[-length(h1$breaks)]),
           main=paste("Clustered Occupancies", lmcmcRes$groupID ),
           xlab = "Prob. of cluster membership (pClust)"
           
           )
   
   txtLeg <- c("Exploit","Explore")
   ## Make Legend order match the colour classes
   ##            being Exploit (Cyan), Explore (Yellow)
  muClustAllChain <- as.data.frame(lmcmcRes$mean)#rbind(
  if ( mean(unlist(muClustAllChain[1]) ) > mean(unlist( muClustAllChain[2]) ) )
    txtLeg<- rev(txtLeg)
  ##Add legend colouring Clusters correctly
   legend("topright",legend=txtLeg, fill=clustCol)
}

# Plot probability densities of initiating hunting within each Dispersal cluster  for each group
#  clusterIDOffset, and groupIDOffset plot Allows function to work when multiple subgroups are modelled
# by extracting from these columns pClust[groupID,Clust] : pClust[1,1] pClust[2,1] ... pClust[5,2] pClust[6,2] 
plotHuntProb <- function(lmcmcRes,clustCol,groupIDOffset=1,clustIDOffset=1)
{
  d1 <- density( lmcmcRes$pHunt[[lmcmcRes$chain]][,groupIDOffset] )
  d2 <- density(lmcmcRes$pHunt[[lmcmcRes$chain]][,groupIDOffset + clustIDOffset]) ##The Indexes are organized as such
  plot(d1, lty=1, lwd=3, col=clustCol[1],
                main=paste("Hunt initiation", lmcmcRes$groupID ),
                xlab = "Prob. of hunt initiation per cluster (pHunt)",xlim=c(0,1),ylim=c(0,max(max(max(d2$y),max(d1$y)))*1.10 ))
  lines(d2,lwd=3,lty=2,col=clustCol[2])
  
   txtLeg <- c("Exploit","Explore")
   ## Make Legend order match the colour classes
   ##            being Exploit (Cyan), Explore (Yellow)
  muClustAllChain <- as.data.frame(lmcmcRes$mean)#rbind(
  if ( mean(unlist(muClustAllChain[1]) ) > mean(unlist( muClustAllChain[2]) ) )
    txtLeg<- rev(txtLeg)
  ##Add legend colouring Clusters correctly
   legend("topright",legend=txtLeg, fill=clustCol)
}


# Colour Coded Histogram of Dispersion Data Showing plit between Exploit[1] / Explore[2]
histClusteredDispersion <- function(lmcmcRes,vDispersion,clustCol)
{
  ## Plot Clustered  Histogram 
  breaksSlots <-  seq(0,11,by=0.5)
  h0 <- hist(vDispersion, breaks=breaksSlots,plot=FALSE) # freq=TRUE,
  h1 <- hist(vDispersion[lmcmcRes$clustID == 1], breaks=breaksSlots, plot=FALSE) #xlim=c(0,10),ylim=c(0,max(h0$counts))
  h2 <- hist(vDispersion[lmcmcRes$clustID == 2], breaks=breaksSlots, plot=FALSE)  #xlim=c(0,10),
  
  barplot(rbind(h1$density,h2$density),beside = FALSE, col = c(clustCol,"white"),names.arg = (h1$breaks[-length(h1$breaks)]),main=paste("Clustered densities", lmcmcRes$groupID ),xlab = "Dispersion (mm)")
  
}


# Colour Coded Histogram of Dispersion Data  Showing plit between Exploit[1] / Explore[2] - Using Data frame as input
histClusteredDispersionFrame <- function(datSubDispersion,dispfield="Dispersion")
{
  clustCol <- c(colourClusters[1],colourClusters[2])
  ##Validate Colouring - Fast Cluster - Yellow / Slow Cluster Blue
  muC1 <- mean(datSubDispersion[datSubDispersion$clustID == 1,dispfield],na.rm = TRUE)
  muC2 <- mean(datSubDispersion[datSubDispersion$clustID == 2,dispfield],na.rm = TRUE)
  if (muC1>muC2)
    clustCol <- rev(clustCol)
  
  ## Plot Clustered  Histogram 
  upLim <- round(max(datSubDispersion[,dispfield],na.rm = TRUE))
  breaksSlots <-  seq(0,upLim*1.1,by=upLim/30)
  h0 <- hist(datSubDispersion[,dispfield], breaks=breaksSlots,plot=FALSE) # freq=TRUE,
  h1 <- hist(datSubDispersion[datSubDispersion$clustID == 1,dispfield], breaks=breaksSlots, plot=FALSE) #xlim=c(0,10),ylim=c(0,max(h0$counts))
  h2 <- hist(datSubDispersion[datSubDispersion$clustID == 2,dispfield], breaks=breaksSlots, plot=FALSE)  #xlim=c(0,10),
  
  barplot(rbind(h1$density,h2$density),beside = FALSE, col = c(clustCol,"white"),names.arg = (h1$breaks[-length(h1$breaks)]),
          main=paste("Clustered dispersion", paste(unique( datSubDispersion$groupID),collapse="," ) ),xlab = paste(dispfield))
  
}



## Plot Estimated Mean of each Gaussian
plotClusterMeans <- function(lmcmcRes,clustCol)
{
  
  #hist( mucoeff[[3]],xlim=c(0,10), breaks=20,col=colourDataScheme[[groupID]],main=groupID,xlab = "Sample Means (mm)" )  
  tauClustAllChain <- as.data.frame(lmcmcRes$var)#rbind( as.data.frame(tauOfClustcoeff[[3]]),as.data.frame(tauOfClustcoeff[[2]]),as.data.frame(tauOfClustcoeff[[1]]))
  muClustAllChain <- as.data.frame(lmcmcRes$mean)#rbind( as.data.frame(muOfClustcoeff[[3]]),as.data.frame(muOfClustcoeff[[2]]),as.data.frame(muOfClustcoeff[[1]]) )
  
  ## Plot Estimated Mean of each Gaussian
  plot(density(unlist(muClustAllChain[1]) ) ,xlim=c(0,10),col=clustCol[1],lwd=3,lty=1,main=paste("Cluster means", lmcmcRes$groupID ),xlab = "Estimated means of each cluster (mu)")
  lines(density(unlist(muClustAllChain[2]) ) ,xlim=c(0,10),col=clustCol[2],lwd=3,lty=2)

}

## Compare NegBin To Clustered Data distribution using CDF plots
plotNBFitcdf <- function(vDispersion,resParams)
{
  XLim <- 100
  x <- seq(0,XLim,1)
  ntail <- 20
  clustCol <-c(colourClusters[1],colourClusters[2])
  if ( mean(resParams$mean[,1])  > mean(resParams$mean[,2]) )
    clustCol <- rev(clustCol)
  
  cdfD_C1 <- ecdf(vDispersion[resParams$clustID == 1]*10)
  cdfD_C2 <- ecdf(vDispersion[resParams$clustID == 2]*10)
  plot(cdfD_C1,col="red",pch=5,xlab=NA,ylab=NA,main="",xlim=c(0,XLim),ylim=c(0,1))
  lines(cdfD_C2,col="blue",pch=5,xlab=NA,ylab=NA,main="",xlim=c(0,XLim),ylim=c(0,1))
  ##Construct CDF of Model by Sampling randomly from Model distribution for exp rate parameter
  for (c in 1:2) {
    for (i in (NROW(resParams$q[,1])-ntail):NROW(resParams$q[,1]) )
    {
      cdfM <- dnbinom(x,size=resParams$r[i,c],prob= resParams$q[i,c]  )##1-exp(-q*x) ##ecdf(  dexp( x, q  ) )
      lines(x,cumsum(cdfM),col=clustCol[c],lty=1) #add=TRUE,
    }
  }
  ##Model AND Data Densities
  c<-1
  plot(((dnbinom(x,size=mean(resParams$r[,c] ), prob= mean(resParams$q[,c]))  ) ), col=clustCol[c],lwd=2,main="NB Model and data distributions",xlim=c(0,XLim),ylim=c(0,2*max(cdfM)),type="l",ylab="Density",xlab="Dispersal (mm x 10)")
  lines(density(vDispersion[resParams$clustID == c]*10,na.rm=TRUE), col=clustCol[c],lty=2,lwd=3)
  #hist( dnbinom( x, size=1/mean(resParams$r[,c] ), prob = mean(resParams$q[,c]) ) ,col=colourClusters[c],freq=FALSE,breaks=20)
  #hist(vDispersion[resParams$clustID == c]*10,col=colourClusters[c],freq=FALSE,add=TRUE)
  
  c<-2
  lines((dnbinom(x,size=resParams$r[,c],prob= resParams$q[,c] )),col=clustCol[c],lwd=2)
  lines(density(vDispersion[resParams$clustID == c]*10,na.rm=TRUE),col=clustCol[c],lty=2,lwd=3)
  #hist( dnbinom(x, size=mean(resParams$r[,c] ), prob= mean(resParams$q[,c]) ) ,col=colourClusters[c],freq=FALSE)
  #hist(vDispersion[resParams$clustID == c]*10,col=colourClusters[c],freq=FALSE,add=TRUE)
  legend("topright",legend=c("NB Model","Data"),lty=c(1,2),lw=c(2,3) )
  legend("bottomright",legend=c("Exploit","Explore"),fill=colourClusters)
}

# Plot Clustering Dispersion Results #
# Colour coded Histogram, Prob of cluster membership, mean dispersion per Gaussian cluster 
plotClusterModel <- function(results, vDispersion, groupID, lmcmcRes)
{
  
  muClustAllChain <- as.data.frame(lmcmcRes$mean)#rbind(
  ## Make Colour code match Low/High Dispersal 
  ##            being Exploit (Cyan), Explore (Yellow)
  clustCol <- c(colourClusters[1],colourClusters[2])
  if ( mean(unlist(muClustAllChain[1]) ) > mean(unlist( muClustAllChain[2]) ) )
    clustCol <- rev(clustCol) ##Reverse Colour Order so C1 - has explore colour , and C2 has exploit colour

  histClusteredDispersion(lmcmcRes,vDispersion,clustCol)
  ## Plot Estimated Mean of each Gaussian
  plotClusterMeans(lmcmcRes,clustCol)
  #plot(density(muClustAllChain$`muOfClust[1]`),xlim=c(0,10),col=clustCol[1],lwd=3,lty=1,main=paste("Cluster means", groupID ),xlab = "Estimated means of each cluster (mu)")
  #lines(density(muClustAllChain$`muOfClust[2]`),xlim=c(0,10),col=clustCol[2],lwd=3,lty=2)
  
  ##plot prob of occupying each cluster
  if (groupID != "All")
    plotClusterProb(lmcmcRes,clustCol)
  #breaksProb <- seq(0,1,by=0.01)
  #list_histo <- hist(lmcmcRes$pClustcoeff[[lmcmcRes$chain]],breaks=breaksProb,main=groupID,freq = FALSE)
  #hist( lmcmcRes$pClustcoeff[[lmcmcRes$chain]][,1],xlim=c(0,1),ylim=c(0,max(list_histo$counts)), breaks=breaksProb,col=clustCol[1],xlab = "Prob. of cluster membership (pClust)" ,add=TRUE,freq=FALSE)
  #hist( lmcmcRes$pClustcoeff[[lmcmcRes$chain]][,2],xlim=c(0,1), breaks=breaksProb,col=clustCol[2],main=groupID,add=TRUE,freq=FALSE )
  
}

##plot Cluster Dists

## Evoked


#results <- results.NF.E
#vDispersion <- vDispersion.NF.S
#groupID <- "NL"

```


```{r RJags-model-results-LOAD, eval=FALSE, fig.show='hold', out.width="33%",dev='png',warnings=FALSE,cache=FALSE} 
#ref.label='plot-functions dispersion-clustering'
## Load Gaussian Mixture Clustering Results
#if (!exists("results.NF.E"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_NL.RData') )
#if (!exists("results.NF.S"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_NE.RData') )
#if (!exists("results.LF.E"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_LL.RData') )
#if (!exists("results.LF.S"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_LE.RData') )
#if (!exists("results.DF.E"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_DL.RData') )

   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_DE.RData') )
#if (!exists("resultsGmix.All"))
   load(file=paste0(strDataExportDir,'jagsModelResults_clustDispersion_All.RData') )


plotClusterModel(results.NF.E,vDispersion.NF.E, "NL", getMCMCEstimatedParams(results.NF.E,"NL",2))
plotClusterModel(results.NF.S,vDispersion.NF.S, "NE", getMCMCEstimatedParams(results.NF.S,"NE",2))
```
