---
title: "OliviaFeedingAssay"
author: "Konstantinos Lagogiannis"
date: "23/05/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("config_lib.R")

setEnvFileLocations("HOME") #HOME,OFFICE,#LAPTOP

source("HuntingEventAnalysis_lib.r")

library(RColorBrewer);


mypalette<-brewer.pal(3,"Set1")

colourH <- list(HET= mypalette[2], #rgb(0.9,0.01,0.01,0.2),
                HOM = mypalette[3], #rgb(0.01,0.01,0.9,0.2))
                WT=mypalette[1]) #rgb(0.01,0.7,0.01,0.2),
                
pchH <- list(HET= 1,
                HOM = 16, #rgb(0.01,0.01,0.9,0.2))
                WT=22) #rgb(0.01,0.7,0.01,0.2),

##Load Hunt event data
strHuntEventFile <- "/media/kostasl/D445GB_ext4/kostasl/Dropbox/Calculations/zebrafishtrackerData/out/FeedingAssay/HB_allHuntEvents.rds"
datHuntEvents <-readRDS(strHuntEventFile)

##load Tracked Frames
strdatTrackedFramesFile = "/media/kostasl/D445GB_ext4/kostasl/Dropbox/Calculations/zebrafishtrackerData/out/FeedingAssay/setn1_Dataset_tracking_May2022.rds"

datAllFrames <- readRDS(strdatTrackedFramesFile)

vGroupIDs <- c("WT","HET","HOM") #(unique(datAllFrames$group)) ##Rearing Group names(groupsrcdatList)
vCondIDs <- as.character(unique(datAllFrames$testCond))

```

# Hunt Events

```{r, re-calcHuntStats,echo = FALSE}
##Calc Hunt Stat
lHuntStat     <- list();
i = 0
for (g in vGroupIDs)
{
  for (c in vCondIDs)
  {
    i = i + 1
    message(paste("#### Process Rearing Group ",g," Tested in",c, "###############"))
    lHuntStat[[g]] <- calcHuntStat3(datHuntEvents[datHuntEvents$groupID == g,])
    #lHuntStat[[i]] = calcHuntStat3(datHuntEvent)
    stopifnot(length(lHuntStat[[g]]$vHLarvaEventCount) > 0)
  }
}
datHuntStat = do.call(rbind,lHuntStat)#

message("~~ Finished Summarizing HuntEvent Data For Each Group ~~ ")

```

##  Number of Hunt Events

```{r, hunteventsperGroup, echo = FALSE}

#print(table(datAllHuntEvent$groupID))


boxplot(as.numeric(datHuntStat[vGroupIDs[1],]$vHLarvaEventCount),
        as.numeric(datHuntStat[vGroupIDs[2],]$vHLarvaEventCount),
        as.numeric(datHuntStat[vGroupIDs[3],]$vHLarvaEventCount),
        names = c(vGroupIDs[1],vGroupIDs[2],vGroupIDs[3]),
        col=c(colourH[[vGroupIDs[1]]],colourH[[vGroupIDs[2] ]],colourH[[vGroupIDs[3] ]] ),
        ylab="Number of Hunt events per larva ")

testHEvents =  list(
            WTvsHET = t.test(as.numeric(datHuntStat["WT",]$vHLarvaEventCount),
            as.numeric(datHuntStat["HET",]$vHLarvaEventCount) ),
            WTvsHOM = t.test(as.numeric(datHuntStat["WT",]$vHLarvaEventCount),
            as.numeric(datHuntStat["HOM",]$vHLarvaEventCount) ),
            HOMvsHET = t.test(as.numeric(datHuntStat["HOM",]$vHLarvaEventCount),
            as.numeric(datHuntStat["HET",]$vHLarvaEventCount) )
          )


message("Significance WT vs HET: ", testHEvents$WTvsHET$p.value,
      " mean :", as.numeric(testHEvents$WTvsHET$estimate[1]), 
      " vs ", as.numeric(testHEvents$WTvsHET$estimate[2]) )

message("Significance WT vs HOM: ", testHEvents$WTvsHOM$p.value, " mean :", 
      testHEvents$WTvsHOM$estimate[1]," vs ", testHEvents$WTvsHOM$estimate[2] )
message( "Significance HOM vs HET: ", testHEvents$HOMvsHET$p.value, 
      " mean :", testHEvents$HOMvsHET$estimate[1]," vs ",testHEvents$HOMvsHET$estimate[2])

```

Significance t-test give WT vs HET 


## Timing of Hunt events

How are hunt events distributed during the 20min of prey encounters?
We pool hunt event occurances withing each group and plot the cumulative distribution function across the 20min

```{r hunteventsTiming, echo = FALSE}

plot(ecdf(datHuntEvents[datHuntEvents$groupID == "HET",]$startFrame/(50*60)),col=colourH$HET,pch=pchH$HET,
     main="Cumulative distribution of Hunt events through time",xlab="min")
lines(ecdf(datHuntEvents[datHuntEvents$groupID == "HOM",]$startFrame/(50*60)),col=colourH$HOM,pch=pchH$HOM)
lines(ecdf(datHuntEvents[datHuntEvents$groupID == "WT",]$startFrame/(50*60)),col=colourH$WT,pch=pchH$WT,)
legend("topleft",legend=names(colourH), col=unlist(colourH),pch=unlist(pchH) )
```

##   Hunt-event Duration 

### Total time spent hunting 

```{r hunteventsDuration,echo = FALSE}

t.test(datHuntStat["WT",]$vHDurationPerLarva,datHuntStat["HET",]$vHDurationPerLarva)

c_FrmToMin <- 1/(60*mean(datAllFrames$fps))
boxplot(datHuntStat[vGroupIDs[1],]$vHDurationPerLarva*c_FrmToMin,
        datHuntStat[vGroupIDs[2],]$vHDurationPerLarva*c_FrmToMin,
        datHuntStat[vGroupIDs[3],]$vHDurationPerLarva*c_FrmToMin,
        names = c(vGroupIDs[1],vGroupIDs[2],vGroupIDs[3]),
        col=c(colourH[[vGroupIDs[1]]],colourH[[vGroupIDs[2] ]],colourH[[vGroupIDs[3] ]] ),
        ylab="Total time spent hunting per larva (min)")


testHEvents =  list(
            WTvsHET = t.test(as.numeric(datHuntStat["WT",]$vHDurationPerLarva*c_FrmToMin),
            as.numeric(datHuntStat["HET",]$vHDurationPerLarva*c_FrmToMin) ),
            WTvsHOM = t.test(as.numeric(datHuntStat["WT",]$vHDurationPerLarva*c_FrmToMin),
            as.numeric(datHuntStat["HOM",]$vHDurationPerLarva*c_FrmToMin) ),
            HOMvsHET = t.test(as.numeric(datHuntStat["HOM",]$vHDurationPerLarva*c_FrmToMin),
            as.numeric(datHuntStat["HET",]$vHDurationPerLarva*c_FrmToMin) )
          )


message("Significance WT vs HET: ", testHEvents$WTvsHET$p.value, " mean :",testHEvents$WTvsHET$estimate[1]," vs ",testHEvents$WTvsHET$estimate[2] )
message("Significance WT vs HOM: ", testHEvents$WTvsHOM$p.value, " mean:",testHEvents$WTvsHOM$estimate[1]," vs ",testHEvents$WTvsHOM$estimate[2] )
message("Significance HOM vs HET: ", testHEvents$HOMvsHET$p.value, " mean:",testHEvents$HOMvsHET$estimate[1]," vs ",testHEvents$HOMvsHET$estimate[2] )

```
## Mean hunt-event duration

Combined with number of hunt events we examine mean hunt event duration

```{r durationperhuntevent,echo = FALSE}

```

## Prey Density Change

```{r preyDynamics, echo = FALSE, eval=FALSE}

  ## Plot Prey Dynamics ##
  for (grpID in strCondTags)
  plot(meanf(datAllFrames[datAllFrames$expID == 4,]$PreyCount,k=100),type="l",ylim=c(20,80) )  
  for (fID in unique(datAllFrames$expID) )
    lines(meanf(datAllFrames[datAllFrames$expID == fID,]$PreyCount,k=100),type="l",ylim=c(20,80) )  
```


## Eye Motion

```{r eyemovements,echo = FALSE, eval=TRUE,cache=TRUE}
    ### Make Eye Phase Space Density Plots ##########
  
  for (i in vGroupIDs)
  {
    message(paste("#### Eye ProcessGroup ",i," ###############"))
    
    
    ##Take All larva IDs recorded - Regardless of Data Produced - No Tracks Is Also Data
    #vexpID = unique(filtereddatAllFrames$expID)
    ##Select Larvaof this Group
    
    datAllGroupFrames <- datAllFrames[which(datAllFrames$groupID == i),]
    #Note:A Larva ID Corresponds to A specific Condition ex. NF1E (Same Fish Is tested in 2 conditions tho ex. NF1E, NF1L)
    vexpID = unique(datAllGroupFrames$expID)
    #plotGroupMotion(datAllGroupFrames,lHuntStat[[i]],vexpID)
    #######################################################################
    ###  EYE - PLOT Scatter and Eye Densities #####
    strCond = i;
    source("EyeScatterAndDensities.r")
    #####
  }
```

